---
title: "Final Project"
author: "Alex Jones"
date: "2023-08-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#load packages
library(ggplot2)
library(reshape2)
library(afex)
library(lme4)
library(lmerTest)
library(tidyverse)
```


## Overview

This report aims to assess whether minority children judge contextual racial passing (CRP) similarily to White children. After analyzing basic descriptive statistics, we will test the follwowing prediction:

1. Minority children will rate "switching" as OK more than White children.

```{r load}

#Load raw data
rawData<-read.csv("PBC2 07192023.csv")

#Copy raw data
data<-rawData

```


## Descriptives
```{r descriptives}

#AGE DESCRIPTIVES

summary(data$age_years, na.rm=TRUE)

mean(data$age_years, na.rm=TRUE)  #in years
sd (data$age_years, na.rm=TRUE)

min(data$age_years, na.rm=TRUE) #in years

max(data$age_years, na.rm=TRUE)#in years

median(data$age_years,na.rm=TRUE ) #in years
```

## Racial Analysis

### Prediction 1

Prediciton 1 was unsupported as there is no interaction between race and ratings of OK regarding switching or maitaining their racial identity. 
```{r 1}

data$Condition_2<-as.factor(data$Condition_2)
data$White<-as.factor(data$White)

#logistic regression with race interaction
whiteLog<-glm(OK~Condition_2*White, family="binomial",data=data)
summary(whiteLog)

#Generate Bar Graph
bar1<-ggplot(data=data,
             aes(x=Condition_2,
                 y=OK,
                 fill=White))+
   stat_summary(fun="mean",
               geom="bar",
               position="dodge")+
  scale_x_discrete(labels=c("Maintain", "Switch"))+ 
    labs(x="Condition",
       y="OK Ratings")+
    scale_fill_manual(values=c("yellow","navy"),
                    guide=F) +
  theme_grey(base_size=20)

#Output Bar Graph
bar1


```

