---
title: "Final Project"
author: "Alex Jones"
date: "2023-08-02"
output:
   html_document:
    toc: true
    toc_float: true
    fig_width: 10
    fig_height: 6
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#load packages
library(ggplot2)
library(reshape2)
library(afex)
library(lme4)
library(lmerTest)
library(tidyverse)
```


## Overview

This report aims to assess how children judge Contextual Racial Passing (CRP). After analyzing basic descriptive statistics, we will test the following predictions:

1. Minority children will rate "switching" as OK more than White children.
2. Children will rate those who switch as less trustworthy than those who maintain their identity.

```{r load}

#Load raw data
rawData<-read.csv("PBC2 07192023.csv")

#Copy raw data
data<-rawData

```


## Descriptives
```{r descriptives}

#AGE DESCRIPTIVES

summary(data$age_years, na.rm=TRUE)

mean(data$age_years, na.rm=TRUE)  #in years
sd (data$age_years, na.rm=TRUE)

min(data$age_years, na.rm=TRUE) #in years

max(data$age_years, na.rm=TRUE)#in years

median(data$age_years,na.rm=TRUE ) #in years
```

## Racial Analysis

### Prediction 1

Prediciton 1 was unsupported as there is no interaction between race and ratings of OK regarding switching or maitaining their racial identity. 
```{r 1}

data$Condition_2<-as.factor(data$Condition_2)
data$White<-as.factor(data$White)

#logistic regression with race interaction
whiteLog<-glm(OK~Condition_2*White, family="binomial",data=data)
summary(whiteLog)

#Generate Bar Graph
bar1<-ggplot(data=data,
             aes(x=Condition_2,
                 y=OK,
                 fill=White))+
   stat_summary(fun="mean",
               geom="bar",
               position="dodge")+
  scale_x_discrete(labels=c("Maintain Identity", "Switch Identity"))+ 
    labs(x="Condition",
       y="OK Ratings")+
    scale_fill_manual(values=c("yellow","navy"),
                    guide=F) +
  theme_grey(base_size=20)

#Output Bar Graph
bar1


```

### Prediction 2

Prediction 2 was supported by the t test, as children rated those who switched their identity as less trustworthy than those who maintained their identity.
```{r}

#Run a t-test 
tTest<-t.test(Trust ~ Condition_2, var.equal = TRUE, data=data)
tTest

#Make a graph
box1<-ggplot(data=data,
                aes(x=Condition_2,
                    y=Trust,
                    fill=Condition_2))+
  labs(x="Condition",
       y="Trust")+
  scale_x_discrete(labels=c("Maintain Identity","Switch Identity"))+
  theme_grey(base_size=20)+
  guides(fill="none")+
  geom_boxplot(notch=TRUE)+
  scale_fill_manual(values=c("yellow","navy"))

box1

```

